\begin{song}

\SongTitle{Hey, Soul Sister}{Train}

\begin{headerbox}
\RaiseBoxWithAccents
\textit{Original: +4} \quad
\beatsperchord8 \quad
\textit{Strum:} $\Down\Miss\AccentDown\Up\Miss\Up\AccentDown\Up\Down\Miss\AccentDown\Up\Miss\Up\AccentDown\Up$
\end{headerbox}

\begin{hchordbox}
\ukechord{C}
\ukechord{G}
\ukechord{Am}
\ukechord{Am/G}
\ukechord{F}
\end{hchordbox}

\large

\bigskip

\ch{C} Hey-\ch{G}ay, hey-ay-ay-ay-\ch{Am}ay, hey-ay-ay-ay-\ch{F}ay \par

\bigskip

Your \ch{C}lipstick stains \ch{G} on the front lobe of my \par
\ch{Am}left side brains \ch{F} I knew I wouldn't \par
For\ch{C}get ya, and so I went and \ch{G}let you blow my \ch{Am}mind \ch{F\beats4} \ch{G\beats4} \par

\bigskip

Your \ch{C}sweet moonbeam \ch{G} the smell of you in ev'ry \par
\ch{Am}single dream I \ch{F}dream \par
I knew when we col\ch{C}lided you're the one I have de\ch{G}cided \par
Who's one of my \ch{Am}kind \ch{F\beats4} \ch{G\beats4 } \par

\bigskip

\begin{chorusbox}{\Chorus}
\ch{F}Hey soul sister,  \ch{G\beats4}ain't that Mister \ch{C\beats2}Mister \ch{G\beats2}on the \par
\ch{F}Radio stereo, the \ch{G\beats4}way you move ain't \ch{C\beats2}fair you \ch{G\beats2}know \par
\ch{F}Hey soul sister \ch{G\beats4}I don't wanna \ch{C\beats2}miss a \ch{G\beats2}single \par
\ch{F}Thing you do-oo-\ch{G}oo \par
\end{chorusbox}

\bigskip

To\ch{C}night. Hey-\ch{G}ay, hey-ay-ay-ay-\ch{Am}ay, hey-ay-ay-ay-\ch{F}ay \par

\bigskip

\ch{C}Just in time \ch{G} \par
I'm so glad you have a \ch{Am}one track mind like \ch{F}me \par
You gave my life di\ch{C}rection \par
A gameshow love con\ch{G}nection… we can't de\ch{Am}ny \ch{F\beats4} \ch{G\beats4} \par

\bigskip

I'm \ch{C}so obsessed. \ch{G} My heart is bound to beat right \par
\ch{Am}Out my untrimmed \ch{F}chest \par
I believe in \ch{C}you, like a virgin you're Ma\ch{G}donna \par
And I'm always gonna \ch{Am}wanna blow your \ch{F\beats4}mind \ch{G\beats4} \par

\bigskip

\Chorus

\bigskip

To\ch{C}night. The way you can cut a rug \ch{G}watching you's the only drug I \par
\ch{Am}need. Some gangsta I'm so thug. You're the \ch{F}only one I'm dreamin' of, \par
you \ch{C}see. I can be myself now final\ch{G}ly. In fact there's nothin' I can't \par
\ch{Am}be. I want the \ch{Am/G}world to see you'll \ch{F}be \ch{G}with me \par

\bigskip

\Chorus

\bigskip

\ch{F}Hey soul sister \ch{G\beats4}I don't wanna \ch{C\beats2}miss a \ch{G\beats2}single \par
\ch{F}Thing you do-oo-\ch{G}oo \par

\bigskip

To\ch{C}night. Hey-\ch{G}ay, hey-ay-ay-ay-\ch{Am}ay, hey-ay-ay-ay-\ch{F}ay \par
To\ch{C}night. Hey-\ch{G}ay, hey-ay-ay-ay-\ch{Am}ay, hey-ay-ay-ay-\ch{F\beats2}ay \ch{G\beats2} \par
To\ch{C}night \par

\end{song}
