\begin{song}

\SongTitle{Valerie}{Amy Winehouse}

\begin{headerbox}
\RaiseBoxWithAccents
\textit{Original: +1} \quad
\beatsperchord4 \quad
% \textit{Strum:} $\StaccatoDown\ChuckUp\ChuckDown\StaccatoUp\AccentDown\ChuckUp\StaccatoDown\ChuckUp \Down\Up\StaccatoDown\Up\StaccatoDown\Up\Down\Up$
\textit{Strum:} $\AccentDown\Miss\Miss\Up\Down\Up\AccentDown\Miss \Miss\Up\Down\Up\AccentDown\Miss\Down\Up$
or $\StaccatoDown\Miss\Miss\Up\ChuckDown\Miss\Down\StaccatoUp \Miss\Up\StaccatoDown\Miss\StaccatoDown\Miss\Miss\Miss$
\end{headerbox}

\begin{hchordbox}
\ukechord{A}
\ukechord{D}
\ukechord{Dmaj7}
\ukechord{Em}
\ukechord{Fsharpm}
\ukechord{G}
\end{hchordbox}

\large

\bigskip

Well, some\ch{D\rep2}times, I go out by myself \par
And I look across the \ch{Em\rep2}water \par
And I \ch{D\rep2}think of all the things, what you're doin' \par
And in my head, I paint a \ch{Em\rep2}picture \par

\bigskip

\begin{chorusbox}{\PrechorusAndChorus}
\ch{G}Since I've come on home, well, my \ch{F\#m}body's been a mess \par
And I've \ch{G}missed your ginger hair, and the \ch{F\#m}way you like to dress \par
\ch{G}Won't you come on over? \ch{F\#m}Stop makin' a fool out of \par
\ch{A}me… \ch{A - single strum}Why don't you come on over, \par

\bigskip

Vale\ch{D\rep2}rie? Vale\ch{Em\rep2}rie, Vale\ch{D\rep2}rie, Vale\ch{Em\rep2}rie \par
\end{chorusbox}

\bigskip

Did you \ch{D\rep2}have to go to jail? Put your house on up for sale? \par
Did you get a good \ch{Em\rep2}lawyer? \par
I hope you \ch{D\rep2}didn't catch a tan. I hope you'll find the right man \par
Who'll fix it for \ch{Em\rep2}you \par
And are you \ch{D\rep2}shoppin' anywhere? Changed the colour of your hair? \par
And are you \ch{Em\rep2}busy? \par
And did you \ch{D\rep2}have to pay that fine? That you were dodgin' all the time? \par
Are you still \ch{Em\rep2}dizzy? \par

\bigskip

\PrechorusAndChorus

\bigskip

Well, some\ch{D\rep2}times, I go out by myself \par
And I look across the \ch{Em\rep2}water \par
And I \ch{D\rep2}think of all the things, what you're doin' \par
And in my head, I paint a \ch{Em\rep2}picture \par

\bigskip

\PrechorusAndChorus

\bigskip

Vale\ch{D\rep2}rie? Vale\ch{Em\rep2}rie, Vale\ch{D\rep2}rie, Vale\ch{Em\rep2}rie \par
Why don't you come on over, \ch{Dmaj7}Valerie? \par

\end{song}
