\begin{song}

\SongTitle{All Of Me}{John Legend, abridged}

\begin{headerbox}
\RaiseBoxWithAccents
\textit{Original: +1} \quad
\textit{Verse:} $\Down\Miss\Miss\Up\Miss\Miss\Down\Miss$ \quad
\textit{Chorus:} $\AccentDown\Miss\Down\AccentUp\Miss\Up\AccentDown\Up$
\end{headerbox}

\begin{hchordbox}
\ukechord{Am}
\ukechord{C}
\ukechord{D}
\ukechord{Em}
\ukechord{G}
\end{hchordbox}

\large

\bigskip

\Intro\textbf{:} \ch{Em} \ch{C} \ch{G} \ch{D} \rep2 \par

\bigskip

\ch{Em} What would I \ch{C}do without your smart \ch{G}mouth. Drawing me \ch{D}in, and you kicking me \par
\ch{Em}out? Got my \ch{C}head spinning, \ch{G}no kidding, I \ch{D}can't pin you \par
\ch{Em}down. What's going \ch{C}on in that beautiful \ch{G}mind? I'm on your \ch{D}magical mystery \par
\ch{Em}ride. And I'm \ch{C}so dizzy, don't \ch{G}know what hit me, but \ch{D}I'll be \par

\bigskip

al\ch{Am\rep2}right. My head's under \ch{G}water, but \ch{D}I'm breathing \par
\ch{Am\rep2}fine. You're crazy and \ch{G}I'm out of my \ch{D - single strum}mind \par

\bigskip

'Cause \ch{G\rep2}all of me loves \ch{Em\rep2}all of you \par
Love your \ch{Am\rep2}curves and all your edges. All your \ch{D\rep2}perfect imperfections \par
Give your \ch{G\rep2}all to me, I'll give my \ch{Em\rep2}all to you \par
You're my \ch{Am\rep2}end and my beginning. Even \ch{D\rep2}when I lose I'm winning \par
'Cause I give you \ch{Em}aaa–aaa–\ch{C}aaa–all of \ch{G}me  \ch{D} \par
And you give me \ch{Em}aaa–aaa–\ch{C}aaa–all of \ch{G}you, oh-\ch{D - single strum}oh \par

\bigskip

\ch{Em} How many \ch{C}times do I have to tell \ch{G}you. Even when you're \ch{D}crying you're beautiful \par
\ch{Em}too? The world is \ch{C}beating you \ch{G}down, I'm a\ch{D}round through every \par
\ch{Em}mood. You're my \ch{C}downfall, you're my \ch{G}muse. My worst dis\ch{D}traction, my rhythm and  \par
\ch{Em}blues. I can't stop \ch{C}singing, it's \ch{G}ringing in \ch{D}my head for \par

\bigskip

\ch{Am\rep2}you. Cards on the \ch{G}table. We're \ch{D}both showing \par
\ch{Am\rep2}hearts. Risking it \ch{G}all though it's \ch{D - single strum}hard \par

\bigskip

'Cause \ch{G\rep2}all of me loves \ch{Em\rep2}all of you \par
Love your \ch{Am\rep2}curves and all your edges. All your \ch{D\rep2}perfect imperfections \par
Give your \ch{G\rep2}all to me, I'll give my \ch{Em\rep2}all to you \par
You're my \ch{Am\rep2}end and my beginning. Even \ch{D\rep2}when I lose I'm winning \par
'Cause I give you \ch{Em}aaa–aaa–\ch{C}aaa–all of \ch{G}me  \ch{D} \par
And you give me \ch{Em}aaa–aaa–\ch{C}aaa–all of \ch{G}you \ch{D} \par

\bigskip

I give you \ch{Em}aaa–aaa–\ch{C}aaa–all of \ch{G}me  \ch{D} \par
And you give me \ch{Em}aaa–aaa–\ch{C}aaa–all of \ch{G}you, oh-\ch{D}oh \par

\end{song}
