\begin{song}

\SongTitle{American Pie}{Don McLean, abridged}

\begin{headerbox}
\textit{Verse:} $\Down\Miss\Down\Up\Miss\Up\Down\Up$ \quad
\textit{Chorus:} $\Down\Miss\Down\Up \Separator \Down\Miss\Down\Up \Separator \Down\Up\Down \Separator \Up\Miss\Up\Down\Up$ \quad
\end{headerbox}

\begin{chordbox}
% \ukechord{G} \par
\ukechord{D} \par
\ukechord{Em7} \par
% \ukechord{Am} \par
% \ukechord{C} \par
\ukechord{Em} \par
\ukechord{D7} \par
\ukechord{A7} \par
\end{chordbox}

\normalsize

\bigskip

\note{single strums, slowly} \par
A \ch{G\beats2}long, \ch{D\beats2}long \ch{Em7}time ago \ch{Am} I can still re\ch{C}member \par
How that \ch{Em}music used to \ch{D\rep2}make me smile \par
And \ch{G\beats2}I knew \ch{D\beats2}if I \ch{Em7}had my chance that \ch{Am}I could make those \ch{C}people dance \par
And \ch{Em}maybe they'd be \ch{C}happy for a \ch{D\rep2}while \par

\bigskip

But \ch{Em}February \ch{Am}made me shiver, with \ch{Em}every paper \ch{Am}I'd deliver \par
\ch{C\beats2}Bad news \ch{G\beats2}on the \ch{Am}doorstep, I \ch{C}couldn't take one more \ch{D}step \par
I \ch{G\beats2}can't re\ch{D\beats2}member \ch{Em}if I cried when I \ch{Am}read about his \ch{D}widowed bride \par
\ch{G\beats2}Something \ch{D\beats2}touched me \ch{Em}deep inside the \ch{C}day the \ch{D7}music \ch{G\rep2}died. (So) \par

\bigskip

\begin{chorusbox}{\Chorus}
\ch{G\beats2}Bye, \ch{C\beats2}bye Miss A\ch{G\beats2}merican \ch{*D\beats2}Pie \par
Drove my \ch{G\beats2}Chevy to the \ch{C\beats2}levy but the \ch{G\beats2}levy was \ch{*D\beats2}dry \par
And them \ch{G\beats2}good old \ch{C\beats2}boys were drinkin' \ch{G\beats2}whiskey and \ch{*D\beats2}rye \par
Singin' \ch{Em}this will be the day that I \ch{A7}die, \ch{Em}this will be the day that I \ch{D7\rep2}die \par
\end{chorusbox}

\bigskip

\note{a tempo} \par
\ch{G} Did you write the \ch{Am}book of love and do \ch{C}you have faith in \ch{Am}God above \par
\ch{Em} If the Bible \ch{D\rep2}tells you so? \par
Now do \ch{G\beats2}you be\ch{D\beats2}lieve in \ch{Em}rock and roll? Can \ch{Am}music save your \ch{C}mortal soul? \par
And \ch{Em} can you teach me \ch{A7} how to dance re\ch{D\rep2}al slow? \par

\bigskip

Well I \ch{Em}know that you're in \ch{D}love with him 'cause I \ch{Em}saw you dancin' \ch{D}in the gym \par
You \ch{C\beats2}both kicked \ch{G\beats2}off your \ch{A7}shoes, man I \ch{C}dig those rhythm and \ch{D7}blues \par
I was a \ch{G\beats2}lonely \ch{D\beats2}teenage \ch{Em}broncin' buck with a \ch{Am}pink carnation and a \ch{C}pickup truck \par
But \ch{G\beats2}I knew \ch{D\beats2}I was \ch{Em}out of luck the \ch{C}day the \ch{D7}music \par
\ch{G\beats2}died. \ch{C\beats2} \ch{G\beats2} I started \ch{D7\beats2}singing'... \par

\bigskip

\Chorus \par

\bigskip

Now for \ch{G}ten years we've been \ch{Am}on our own and \ch{C}moss grows fat on a \ch{Am}rolling stone \par
But \ch{Em}that's not how it \ch{D\rep2}used to be. When the \par
\ch{G\beats2}jester \ch{D\beats2}sang for the \ch{Em}king and queen in a \ch{Am}coat he borrowed \ch{C}from James Dean \par
In a \ch{Em}voice... that \ch{A7}came from you and \ch{D\rep2}me \par

\bigskip

And \ch{Em}while the king was \ch{D}looking down, the \ch{Em}jester stole his \ch{D}thorny crown \par
The \ch{C\beats2}courtroom \ch{G\beats2}was ad\ch{A7}journed, \ch{C}no verdict was \ch{D7}returned \par
And while \ch{G\beats2}Lennon \ch{D\beats2}read a \ch{Em}book on Marx, the \ch{Am}quartet practiced \ch{C}in the park \par
And \ch{G\beats2}we sang \ch{D\beats2}dirges \ch{Em}in the dark, the \ch{C}day the \ch{D7}music \par
\ch{G\beats2}died. \ch{C\beats2} \ch{G\beats2} We were \ch{D7\beats2}singing'... \par

\bigskip

\Chorus \par

\bigskip

I \ch{G\beats2}met a \ch{D\beats2}girl who \ch{Em7}sang the blues and I \ch{Am}asked her for some \ch{C}happy news \par
But \ch{Em}she just smiled and \ch{D\rep2}turned away \par
I \ch{G\beats2}went down \ch{D\beats2}to the \ch{Em7}sacred store where I'd \ch{Am}heard the music \ch{C}years before \par
But the \ch{Em}man there said the \ch{C}music wouldn't \ch{D\rep2}play \par

\bigskip

And \ch{Em}in the streets the \ch{Am}children screamed, the \ch{Em}lovers cried and the \ch{Am}poets dreamed \par
But \ch{C\beats2}not a \ch{G\beats2}word was \ch{Am}spoken, the \ch{C}church bells all were \ch{D}broken \par
And the \ch{G\beats2}three men \ch{D\beats2}I ad\ch{Em}mire most, the \ch{Am}Father, Son, and the \ch{D}Holy Ghost \par
They \ch{G\beats2}caught the \ch{D\beats2}last train \ch{Em}for the coast the \ch{C}day the \ch{D7}music \par
\ch{G\rep2}died. And they were singing'... \par

\bigskip

\Chorus \par
\note{play instead of the last line} \par
Singin' \ch{C\beats2}this will be the \ch{D7\beats2}day that I \ch{G-C-G}die. \par

\end{song}