\begin{song}

\SongTitle{I'm Yours}{Jason Mraz}

\begin{headerbox}
\RaiseBoxWithAccents
\beatsperchord4\rep2 \quad
\textit{Original: -1} \quad
\textit{Strum:} $\ChuckDown\Miss\AccentDown\StaccatoUp\Miss\ChuckUp\AccentDown\StaccatoUp$
\end{headerbox}


\begin{hchordbox}
\ukechord{Am}
\ukechord{C}
\ukechord{D7}
\ukechord{F}
\ukechord{G}
\end{hchordbox}

\bigskip

\normalsize

Well, \ch{C}you done done me and you bet I felt it \par
I \ch{G}tried to be chill but you're so hot that I melted \par
I \ch{Am}fell right through the cracks \par
And now I'm \ch{F}tryin' to get back \par
Before the \ch{C}cool done run out, I'll be giving it my bestest \par
And \ch{G}nothin's gonna stop me but divine intervention \par
I \ch{Am}reckon it's again my turn \par
To \ch{F}win some or learn some \par

\bigskip

But \ch{C}I won't hesi\ch{G}tate no more, no \ch{Am}more. It cannot \ch{F}wait \par
I'm you\ch{C}rs \ch{G} \ch{Am} \ch{F} \par

\bigskip

\ch{C} Well, open up your mind and see like \ch{G}me. Open up your plans and damn you're \par
\ch{Am}free. Look into your heart and you'll find \ch{F}love, love, love, love \par
\ch{C}Listen to the music of the moment. People dance and \ch{G}sing \par
We're just one big fami\ch{Am}ly. And it's our god-forsaken right to be \ch{F}loved, loved, loved, loved \par
\ch{D7 - single strum}Loved \par

\bigskip

So \ch{C}I won't hesi\ch{G}tate no more, no \ch{Am}more. It cannot \ch{F}wait, I'm sure \par
There's no \ch{C}need to compli\ch{G}cate. Our time is \ch{Am}short. This is our \ch{F}fate. I'm yours \par

\bigskip

\ch{C\beats4} Do, do, do, do you, \ch{G\beats4} but do you, do you, do, \ch{Am\beats4}do, but do you want to come on? \ch{G\beats4} \par
Scooch on over \ch{F}closer, dear. And I will nibble your \ch{D7}ear \par

\bigskip

\ch{C\beats4} \ch{G\beats4} \ch{Am\beats4} \ch{G\beats4} \ch{F} \ch{D7} \par

% A-soo-da-ba-ba-ba-ba-bum \par
% Whoa-oh-oh \par
% Whoa-oh-oh-oh-oh-whoa-whoa-whoa \par
% Uh-huh, mmm-hmm \par

\bigskip

I've been spending \ch{C}way too long checking my tongue in the mirror \par
And \ch{G}bending over backwards just to try to see it clearer \par
But \ch{Am}my breath fogged up the glass \par
And so I \ch{F}drew a new face and I laughed \par
I \ch{C}guess what I'll be saying is there ain't no better reason \par
To \ch{G}rid yourself of vanities and just go with the seasons \par
It's \ch{Am}what we aim to do \par
Our \ch{F}name is our virtue \par

\bigskip

But \ch{C}I won't hesi\ch{G}tate no more, no \ch{Am}more. It cannot \ch{F}wait \par

\bigskip

I'm you\ch{C}rs. Well, open up your mind and see like \ch{G}me. Open up your plans and damn you're \par
\ch{Am}free. Look into your heart and you'll find that \ch{F} the sky is yours \par
So \ch{C}please don't, please don't, please don't. There's no \ch{G}need to complicate \par
'Cause our \ch{Am}time is short. This oh, this oh, this is our \ch{F}fate \par
I'm you\ch{D7 - single strum}rs \par

\end{song}