\begin{song}

\SongTitle{Lemon Tree}{Fool's Garden}

\beatsperchord4 \quad
\textit{Verse:} $\Down\Miss\AccentDown\Up \Down\Miss\AccentDown\Up$ \quad
\textit{Chorus:} $\Down\Miss\Down\Up\Miss\Up\Down\Up$ \quad
\textit{Original: +4}

\normalsize

\begin{chordbox}
\ukechord{Dm} \par
\ukechord{Am} \par
\ukechord{Gm} \par
\ukechord{F} \par
\ukechord{C} \par
\ukechord{C7} \par
\ukechord{Bb} \par
\ukechord{Bdim} \par
\ukechord{A} \par
\end{chordbox}

\large

% [Intro] \par
% \Intro \ch{Dm} \ch{Am} \ch{Dm} \ch{Am} \ch{Gm} \ch{Am} \ch{Dm} \ch{Am} \ch{Dm} \par

\bigskip

I'm \ch{Dm}sitting here in a \ch{Am}boring room, \par
It's \ch{Dm}just another rainy Sunday \ch{Am}afternoon. \par
I'm \ch{Dm}wasting my time, I got \ch{Am}nothing to do. \par
I'm \ch{Dm}hanging around, I'm \ch{Am}waiting for you, \par
But \ch{Gm}nothing ever happens - \ch{Am} and I \ch{Dm\beats2}wonder. \ch{Am\beats2} \ch{Dm} \par

\bigskip

I'm \ch{Dm}driving around \ch{Am}in my car, \par
I'm \ch{Dm}driving too fast, I'm \ch{Am}driving too far. \par
I'd \ch{Dm}like to change my \ch{Am}point of view \par
I \ch{Dm}feel so lonely, I'm \ch{Am}waiting for you \par
But \ch{Gm}nothing ever happens - \ch{Am} and I \ch{Dm\beats2}wonder. \ch{Am\beats2} \ch{Dm} \par

\bigskip

\begin{chorusbox}{\Chorus}
I \ch{F}wonder how, I \ch{C}wonder why \par
\ch{Dm}yesterday you told me 'bout the \ch{Am}blue blue sky \par
And \ch{Bb}all that I can \ch{C}see is just a yellow \ch{F}lemon tree. \ch{C} \par

\bigskip

I'm \ch{F}turning my head \ch{C}up and down, \par
I'm \ch{Dm}turning turning turning turning \ch{Am}turning around \par
And \ch{Bb}all that I can \ch{Bdim}see is just another\ch{C} lemon tree. \ch{C7} \par
\end{chorusbox}

\bigskip

\ch{Dm}Dap \ch{Am} dadada-dap \ch{Dm}didap-da \ch{Am}dadada-dap \par
\ch{Gm}Didap-da \ch{Am} da-didli \ch{Dm\beats2}da \ch{Am\beats2} \ch{Dm} \par

\bigskip

I'm \ch{Dm}sitting here, I \ch{Am}miss the power. \par
I'd \ch{Dm}like to go out, \ch{Am}takin' a shower, \par
But \ch{Dm}there's a heavy cloud in\ch{Am}side my head. \par
I \ch{Dm}feel so tired, put my\ch{Am}self into bed, \par
Where \ch{Gm}nothing ever happens - \ch{Am} and I \ch{Dm\beats2}wonder. \ch{Am\beats2} \ch{Dm} \par

\bigskip

\ch{A\rep2} Isolation - \ch{Dm\rep2}Is not good for me. \par
\ch{C\rep2} Isolation - \ch{F}I don't want to \ch{A} sit on a lemon tree. \par

\bigskip

I'm \ch{Dm}stepping around in a \ch{Am}desert of joy, \par
\ch{Dm}baby anyhow I'll get a\ch{Am}nother toy \par
And \ch{Gm}everything will happen - \ch{Am} and you \ch{Dm\beats2}wonder. \ch{Am\beats2} \ch{Dm} \par

\bigskip

\Chorus

\bigskip

I \ch{F}wonder how, I \ch{C}wonder why \par
\ch{Dm}yesterday you told me 'bout the \ch{Am}blue blue sky \par
And \ch{Bb}all that I can \ch{C}see, \par
And \ch{Bb}all that I can \ch{C}see, \par
And \ch{Bb}all that I can \ch{C}see is just a yellow \ch{F - single strum}lemon tree. \par

\end{song}
