\begin{song}

\SongTitle{Mamma Mia}{ABBA}

\beatsperchord4 \quad

\large

\begin{chordbox}
\ukechord{A} \par
\ukechord{Bm} \par
\ukechord{C} \par
\ukechord{D} \par
\ukechord{Daug} \par
\ukechord{Em} \par
\ukechord{Fsharpm} \par
\ukechord{G} \par
\end{chordbox}

\large

\bigskip

\Intro\textbf{:} \ch{D} \ch{*Daug} \ch{D} \ch{*Daug} \par

\bigskip

\ch{D\rep2}I've been cheated by you, since I don't know \ch{G\rep2}when \par
\ch{D\rep2}So I made up my mind, it must come to an \ch{G\rep2}end \par
\ch{D}Look at me now, \ch{*Daug} will I ever learn? \par
\ch{D}I don't know how, \ch{*Daug} but I suddenly \par
\ch{G\rep2}Lose control, there's a fire with\ch{A}in my soul. \ch{A\beats2} \par


\bigskip
\begin{chorusbox}{\PrechorusAndChorus}
\ch{G\beat}Just \ch{D\beat}one \ch{A}look and I can hear a bell ring \ch{A\beats2} \par
\ch{G\beat}One \ch{D\beat}more \ch{A\rep2}look and I forget everything \par

\bigskip

\ch{D\rep2} Mamma mia, here I go again \par
\ch{N/C\beat} \ch{C\beat}My  \ch{G\beats4}my, how can I re\ch{D\beats2}sist you? \par
\ch{D\rep2} Mamma mia, does it show again? \par
\ch{N/C\beat} \ch{C\beat}My  \ch{G\beats4}my, just how much I've \ch{D\beats2}missed you \par
\end{chorusbox}

\smallskip

\begin{chorusbox}{\Bridge}
\ch{D}Yes, I've been \ch{A}brokenhearted \par
\ch{Bm}Blue since the \ch{F\#m}day we parted \par
\ch{N/C\beat} \ch{C\beat}Why, \ch{G\beats2}why \ch{Em\beats2}did I ever \ch{A\beats2}let you go? \par
\ch{D} Mamma mia, \ch{Bm} now I really know, \par
\ch{N/C\beat} \ch{C\beat}My \ch{G\beats2}my, \ch{Em\beats2}I could never \ch{A\beats2}let you go \par
\end{chorusbox}

\bigskip

\Instrumental\textbf{:} \ch{D} \ch{*Daug} \ch{D} \ch{*Daug} \par

\bigskip

\ch{D\rep2}I've been angry and sad about the things that you \ch{G\rep2}do \par
\ch{D\rep2}I can't count all the times that I've told you we're \ch{G\rep2}through \par
\ch{D}And when you go, \ch{*Daug} when you slam the door \par
\ch{D}I think you know, \ch{*Daug} that you won't be \par
a\ch{G\rep2}way too long... You know that I'm \ch{A}not that strong \ch{A\beats2} \par

\bigskip

\PrechorusAndChorus

\bigskip

\ch{D}Yes, I've been \ch{A}brokenhearted \par
\ch{Bm}Blue since the \ch{F\#m}day we parted \par
\ch{N/C\beat} \ch{C\beat}Why, \ch{G\beats2}why \ch{Em\beats2}did I ever \ch{A\beats2}let you go? \par

\bigskip

\ch{D\rep2}Mamma mia, even if I say \par
\ch{N/C\beat} \ch{C\beat}Bye \ch{G\beats4}bye, leave me now or \ch{D\beats2}never \par
\ch{D\rep2}Mamma mia, it's a game we play \par
\ch{N/C\beat} \ch{C\beat}Bye \ch{G\beats4}bye doesn't mean for\ch{D\beats2}ever \par

\bigskip

\ch{D\rep2}Mamma mia, here I go again \par
\ch{N/C\beat} \ch{C\beat}My  \ch{G\beats4}my, how can I re\ch{D\beats2}sist you? \par
\ch{D\rep2}Mamma mia, does it show again? \par
\ch{N/C\beat} \ch{C\beat}My  \ch{G\beats4}my, just how much I've \ch{D\beats2}missed you \par

\bigskip

\Bridge

\bigskip

\Outro\textbf{:} \ch{D} \ch{*Daug} \ch{D} \ch{*Daug} (repeat and fade out) \par

\end{song}
