\begin{song}

\SongTitle{Summer of '69}{Bryan Adams}

\begin{headerbox}
\RaiseBoxWithAccents
\textit{Original: +7} \quad
\textit{Strum:} $\Down\Miss\ChuckDown\AccentUp\Miss\Up\ChuckDown\Up$
\end{headerbox}

\begin{hchordbox}
\ukechord{Bb}
\ukechord{C}
\ukechord{D}
\ukechord{Eb}
\ukechord{Em}
\ukechord{F}
\ukechord{G}
\end{hchordbox}

\large

\bigskip

\ch{G\rep2} I got my first real six-string. \ch{D\rep2} Bought it at the Five and Dime \par
\ch{G\rep2} Played it till my fingers bled. \ch{D\rep2} It was the summer of sixty-nine \par

\bigskip

\ch{G\rep2} Me and some guys from school \ch{D\rep2} had a band and we tried real hard \par
\ch{G\rep2} Jimmy quit, Jodie got married. \ch{D\rep2} Shoulda known, we’d never get far \par

\bigskip

\ch{Em} Oh, when I \ch{D}look back now \ch{G} that summer seemed to \ch{C}last forever \par
\ch{Em} And if I \ch{D}had the choice, \ch{G} yeah I’d always \ch{C}wanna be there \par
\ch{Em} Those were the \ch{D - single strum}best days of my \par
\ch{G\rep2}Life \ch{D\rep2} \ch{G\rep2} \ch{D\rep2} \par

\bigskip

\ch{G\rep2} Ain’t no use in complainin’ \ch{D\rep2} when you’ve got a job to do \par
\ch{G\rep2} Spent my evenin’s down at the drive-in \ch{D\rep2} and that’s when I met you, yeah \par

\bigskip

\ch{Em} Standin’ on your \ch{D}mama’s porch, \ch{G} you told me that you’d \ch{C}wait forever \par
\ch{Em} Oh and when you \ch{D}held my hand \ch{G} I knew that it was \ch{C}now or never \par
\ch{Em} Those were the \ch{D - single strum}best days of my \par
\ch{G\rep2}Life… oh \ch{D\rep2}yeah! Back in the summer of \ch{G\rep2}sixty-nine \ch{D\rep2} \par

\bigskip

\ch{Bb} Man we were \ch{Eb}killin’ time \par
We were \ch{F}young and restless, we \ch{Eb}needed to unwind \par
\ch{Bb} I guess \ch{Eb}nothin’ can last for\ch{F\rep2}ever… forever… no \par
\ch{G\rep2}Yeah! \ch{D\rep2} \ch{G\rep2} \ch{D\rep2} \par

\bigskip

\ch{G\rep2} And now the times are changin’. \ch{D\rep2} Look at everything that’s come and gone \par
\ch{G\rep2} Sometimes when I play that old six-string \ch{D\rep2} think about ya, wonder what went wrong \par

\bigskip

\ch{Em} Standin’ on your \ch{D}mama’s porch, \ch{G} you told me it would \ch{C}last forever \par
\ch{Em} Oh the way you \ch{D}held my hand \ch{G} I knew that it was \ch{C}now or never \par
\ch{Em} Those were the \ch{D - single strum}best days of my \par
\ch{G\rep2}Life… oh \ch{D\rep2}yeah! Back in the summer of \ch{G\rep2}sixty-nine \ch{D\rep2} \par
It was the summer of \ch{G\rep2}sixty-nine. Oh \ch{D\rep2}yeah \ch{G\rep2} \ch{D\rep2} \par
\ch{G - single strum} \par

\bigskip

\bigskip

\bigskip

{\it\smaller
Tip: Play \textbf{Gsus2-G-Gsus4-G-Gsus2-G\ \ Dsus2-D-Dsus4-D-Dsus2-D} after choruses and the bridge.
}


\end{song}
