\begin{song}

\SongTitle{Sweet Child O' Mine}{Guns N' Roses}

\begin{headerbox}
\RaiseBoxWithAccents
\beatsperchord4 \quad
\textit{Original: +1} \quad
\textit{Strum:} $\AccentDown\Miss\Down\Miss\Down\Miss\AccentDown\Miss \Down\Miss\Down\Miss\AccentDown\Miss\Down\Up$ double time
\end{headerbox}

\begin{vchordbox}
\ukechord{A}
\ukechord{Bb}
\ukechord{C}
\ukechord{Dm}
\ukechord{F}
\ukechord{G}
\ukechord{Gm}
\end{vchordbox}

\large

\bigskip

\ch{C} \ch{Bb} \ch{F} \ch{C} \rep2 \par

\bigskip

\ch{C\rep2}She's got a smile that it seems to me \par
Re\ch{Bb\rep2}minds me of childhood memories \par
Where \ch{F\rep2}everything was as fresh as the bright blue \ch{C\rep2}sky \par
\ch{C\rep2}Now and then, when I see her face \par
She \ch{Bb\rep2}takes me away to that special place \par
And if I \ch{F\rep2}stared too long… I'd probably break down and \ch{C\rep2}cry \par

\bigskip

\ch{G}Whoah, oh-oh-\ch{Bb}oh, sweet child o' \ch{C\rep2}mine \par
\ch{G}Whoah, oh-oh-\ch{Bb}oh, sweet love o' \ch{C\rep2}mine \par

\bigskip

\textit{(Do-}\ch{C\rep2}\textit{do-doo…)} \ch{Bb\rep2} \ch{F\rep2} \ch{C\rep2} \par

\bigskip

\ch{C\rep2}She's got eyes of the bluest skies \par
As \ch{Bb\rep2}if they… thought of rain \par
I \ch{F\rep2}hate to look into those eyes \par
And \ch{C\rep2}see an ounce of pain \par
Her \ch{C\rep2}hair reminds me of a warm safe place \par
Where \ch{Bb\rep2}as a child I'd hide \par
And \ch{F\rep2}pray for the thunder… and the rain \par
To \ch{C\rep2}quietly pass me by \par

\bigskip

\ch{G}Whoah, oh-oh-\ch{Bb}oh, sweet child o' \ch{C\rep2}mine \par
\ch{G}Whoah, oh-oh-\ch{Bb}oh, sweet love o' \ch{C\rep2}mine \par
\ch{G}Whoah, oh-oh-\ch{Bb}oh, sweet child o' \ch{C\rep2}mi-i-i-ine, oh yeah \par
\ch{G}Whoah, oh-oh-\ch{Bb}oh, sweet love o' \ch{C\rep2}mine \par

\bigskip

\instruction{guitar solo} \par
\ch{Dm} \ch{Bb} \ch{A} \ch{Gm} \rep2 \par

% \instruction{guitar solo} \par
% \ch{Dm} \ch{Bb} \ch{A} \ch{Gm} \rep4 \par
% \ch{Dm} \ch{F} \ch{G} \ch{Bb\beats2} \ch{C\beats2} \rep4 \par

\bigskip

\ch{Dm}Where do we go, \ch{F}where do we go now \par
\ch{G}Where do we go  \ch{Bb\beats2} \ch{C\beats2} \par
\ch{Dm}Where do we go, \ch{F}where do we go \par
\ch{G}Where do we go now \ch{Bb\beats2} \ch{C\beats2} \par
\ch{Dm}Where do we go \ch{F} \vocals{sweet child} \par
\ch{G}Where do we go now \ch{Bb\beats2} \ch{C\beats2} \par
\ch{Dm}Ay ay ay ay \ch{F}ay ay ay ay \par
\ch{G}Where do we go now, ah-\ch{Bb\beats2}ah-ay, ah-\ch{C\beats2}ah-ay-ah \par

\bigskip

\ch{Dm}Where do we go? \ch{F} \par
\ch{G}Where do we go now? \ch{Bb\beats2} \ch{C\beats2} \par
\ch{Dm}Where do we go? \ch{F} \par
\ch{G}Where do we go now? \ch{Bb\beats2} \ch{C\beats2} \par

\ch{Dm}Where do we go? \ch{F} \par
\ch{G}Where do we go now? \ch{Bb\beats2}No-no-no \ch{C\beats2}no-no-no \par
\ch{Dm}No, sweet \ch{F}child \par
Sweet \ch{G}chi-i-\ch{Bb\beats2}i-i-\ch{C\beats2}i-ild of \ch{Dm}mi-i-ine \par

\end{song}
