\begin{song}

\SongTitle{What's Up}{4 Non Blondes}

\begin{headerbox}
\RaiseBoxWithAccents
\beatsperchord4 \quad
\textit{Original: +2} \quad
\textit{Strum:} $\AccentDown\Miss\Down\Up\AccentDown\Miss\Down\Up\AccentDown\Up\Down\AccentUp\Miss\Up\AccentDown\Up$ double time
\end{headerbox}

\begin{vchordbox}
\ukechord{Am}
\ukechord{C}
\ukechord{G}
\end{vchordbox}

\Large

\bigskip

\ch{G}25 years of my life and still \par
\ch{Am}Trying to get that… great big hill of \par
\ch{C}Hope… for a desti\ch{G}nation \par

\bigskip

I \ch{G}realised quickly when I knew I should \par
That the \ch{Am}world was made for this… brotherhood \par
Of \ch{C}man… For whatever that \ch{G}means \par

\bigskip

\begin{chorusbox}{\Chorus}
And so I \ch{G}cry sometimes when I'm lying in bed \par
Just to \ch{Am}get it all out, what's in my head \par
And I, \ch{C} I'm feeling \par
A little pe\ch{G}culiar \par

\bigskip

And so I \ch{G}wake in the morning and I step outside \par
And I \ch{Am}take deep breath and I get real high \par
And I \ch{C} scream to the top of my lungs \par
What's goin' \ch{G}on? \par

\bigskip

And I say \ch{G}hey-yeah-yeah-ye-ah, \ch{Am}hey-yeah-yeah \par
I say \ch{C}hey, what's goin' \ch{G}on? \par
And I say \ch{G}hey-yeah-yeah-ye-ah, \ch{Am}hey-yeah-yeah \par
I say \ch{C}hey, what's goin' \ch{G}on? \par
\end{chorusbox}

\bigskip

\ch{G} Ooh, ooh \ch{Am} oo-oo-oo-oo-ooh \ch{C} oo-oo-oo-oo-ooh \ch{G} \par
\ch{G} Ooh, o-o-oh \ch{Am} oo-oo-oo-oo-ooh \ch{C} oo-oo-oo-oo-ooh \ch{G} \par

\bigskip

And I \ch{G}try \par
Oh my God do I \ch{Am}try \par
I try all the \ch{C}time \par
In this insti\ch{G}tution \par

\bigskip

And I \ch{G}pray \par
Oh my God do I \ch{Am}pray \par
I pray every single \ch{C}day \par
For revo\ch{G}lution \par

\bigskip

\Chorus

\bigskip

\ch{G}25 years of my life and still \par
\ch{Am}Trying to get that… great big hill of \par
\ch{C}Hope… for a desti\ch{G}nation \par

\bigskip

\end{song}
